Overview

### 2023-12-26 README.Rmd
Add pkgdown fix #79
Declutter

# oolong <img src="man/figures/oolong_logo.svg" align="right" height="200" />

@@

Please refer to the [overview](overview_gh.md) for an introduction to this package. If you need to deploy the test online, please refer to the [Deployment Vignette](deploy_gh.md). If you use BTM, please refer to the [BTM Vignette](btm_gh.md).

>>>>

# oolong <img src="man/figures/oolong_logo.png" align="right" width="120" />

@@

Please refer to the [overview](https://gesistsa.github.io/oolong/articles/overview.html) for an introduction to this package. If you need to deploy the test online, please refer to the [Deployment Vignette](https://gesistsa.github.io/oolong/articles/deploy.html). If you use BTM, please refer to the [BTM Vignette](https://gesistsa.github.io/oolong/articles/btm.html).
